Notes on area-length problem for CLE

### 2013-09-11 area-length/notes.tex
Minor changes

@@

Consider loop of length $L$. The radius of the loop is connected with
the length as $L\sim R^{d_H}$. The area is related to radius $A\sim
R^2$, so $A\sim L^{\frac{2}{d_H}$.
(It is proved or almost proved in papers by Lawler).

@@

@@

>>>>

\subsection{$O(n)$ model}
\label{sec:introduction-1}

Partition function for $O(n)$ model is
\begin{equation}
  \label{eq:9}
  Z_{O(n)} = \sum_{\mbox{loop conf}} x^{\mbox{total length}}
  n^{\mbox{number of loops}}
\end{equation}

@@

Consider loop of length $L$. The radius of the loop is connected with
the length as $L\sim R^{d_H}$. The area is related to radius $A\sim
R^2$, so $A\sim L^{\frac{2}{d_H}}$.
(It is proved or almost proved in papers by Lawler).

@@

Partition function is product over loops of different length
\begin{equation}
  \label{eq:10}
  Z_{O(n)} = \sum_{\mbox{loop conf}} \prod_L x^{L N(L)} n^{N(L)} = \sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}
\end{equation}

We can rewrite $G^r(\mu,x)$ as the derivative of generating function
\begin{equation}
  \label{eq:7}
  G^r(\mu,x)=\mu\partial_x \log Z(\mu,\mu_B)
\end{equation}

Here
\begin{equation}
  \label{eq:8}
  Z(\mu,\mu_B) = \left< e^{-\mu A} \right> = \frac{\sum_{\mbox{loop conf}}
  \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)} e^{-\mu A}}{\sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}}
\end{equation}

@@

Boundary Liouville theory:
\begin{equation}
  \label{eq:12}
  S=\oint_{S^{1}} \phi \mathcal{N} \phi |dw| + \oint_{S^{1}} \mu_{B} e^{b\phi} + \mu\int_{D} e^{2b\phi} dw d\bar{w}
\end{equation}

\begin{equation}
  \label{eq:11}
  G^{r}(\mu,\mu_{B}) = \mu \frac{\left<V_{\frac{b}{2}} B_{-\frac{1}{b}}\right>}{\left<V_{\frac{b}{2}}\right>}
\end{equation}
